A parametric system for adaptive extrusion width contour parallel toolpath generation

### 2019-08-21 4_method.tex
redo surface construction

\subsection{Surface construction}\label{sec_surface_construction}
The shape decomposition we employ on the outline shape of a layer is based on a common skeletonization of the polygonal outline shape: the medial axis.
Starting from the medial axis we further decompose the shape into simple fragments, so that we can easily process the shape using piecewise linear approximations.

@@

Alternatively the medial axis can be defined as the locations where the union of cones on the boundary shape is discontinuous,
or it can be defined as the locations where wave-front propagating from the outline shape make sharp corners. \cite{blum1967transformation}
This last interpretation is especially relevant because the naive toolpath generation method consists precisely in equidistant wave-fronts from the outline.
The medial axis can therefore be seen as the space within which contour following toolpaths are generated.
See \cref{MAT_explanation}.

@@

\begin{figure}
\centering
\begin{subfigure}{0.3\columnwidth}
\centering
\includegraphics[height=1.5\columnwidth]{sources/method/MAT_explanation_circles.pdf}
\caption{Circles}
\label{MAT_explanation_circles}
\end{subfigure}
\begin{subfigure}{0.3\columnwidth}
\centering
\includegraphics[height=1.5\columnwidth]{sources/method/MAT_explanation_wavefronts.pdf}
\caption{Wave-fronts}
\end{subfigure}
\begin{subfigure}{0.3\columnwidth}
\centering
\includegraphics[height=1.5\columnwidth]{sources/method/MAT_explanation_cones.pdf}
\caption{Cones}
\end{subfigure}
\caption{
Medial axis representations.
The medial axis can be defined in terms of the the number of support points of the inscribed circles,
as the pinch sites in wave-fronts
or as ridges in a volume defined by the union of cones.
}
\label{MAT_explanation}
\end{figure}

\begin{figure}
\begin{subfigure}{0.3\columnwidth}
\centering
%\includegraphics[height=1.5\columnwidth]{sources/method/MAT_explanation_shape_decomposition.pdf}
\includegraphics[height=1.5\columnwidth]{sources/method/half_edge_datastructure.pdf}
\caption{Simple case}
\label{shape_decomposition_simple}
\end{subfigure}
\begin{subfigure}{0.65\columnwidth}
\includegraphics[width=\columnwidth]{sources/method/MAT_VD_VQ.pdf}
\caption{Complex case employing discretization}
\label{shape_decomp_complex}
\end{subfigure}
\caption{
Skeletonization of an outline shape (black).
Relation between the medial axis (red), the limited Voronoi Diagram (red and green) and the Skeletal Trapezoidation (red, green and gray): MAT $\subset$ Limited VD $\subset$ ST.
}
\label{skeletonization_comparison}
\end{figure}

\begin{figure} \centering
\includegraphics[width=.75\columnwidth]{sources/method/mat_3d_blender_render.png}
\caption{
Visualization of the distance field function as captured by the skeletal trapezoidation.
}
\label{mat_3d}
\end{figure}

\subsubsection{Skeletal trapezoidation}
We employ a shape decomposition proposed by \citeauthor{Ding2016a} which starts from the medial axis and further decomposes the outline shape into simple fragments. \cite{Ding2016a}
Each of the regions demarcated by the skeleton is further decomposed by adding radial bones from each node $v$ to its support $\text{sup}(v)$.
The resulting skeleton decomposes the outline shape into trapezoids and triangles.
We will therefore call this shape decomposition the \emph{Skeletal Trapezoidation} (ST).
(The concept of a trapezoidation conventionally allows for the degenerate case where a trapezoid resolves into a triangle. \cite{chazelle1984,fournier1984})
We represent such a skeleton in a standard half-edge data-structure.
See \cref{shape_decomposition_simple}.

@@

We then also discretize parabolic segments and segments generated by two concave outline vertices into segments approximately as long as some constant $d^\text{discretization}$.
See \cref{discretization} and \cref{shape_decomp_complex}.
That way we can approximate the feature radius $R$ in between the two nodes $v_0$ and $v_1$ of a bone in the ST by interpolating linearly between $R(v_0)$ and $R(v_1)$.
This makes the skeleton capture a discrete approximation of the radius function which can then be used to create a triangulated 3D model of the conical representation of the medial axis; see \cref{mat_3d}.

>>>>

\subsection{Surface construction}\label{sec_surface_construction}
The union of cones surface mesh can be derived from a common skeletonization of the polygonal outline shape: the medial axis.
By assigning each node in the skeleton a height equal to the radial distance to the outline we obtain the shape of the UoC.
Starting from the medial axis we further decompose the shape into simple fragments, so that the mesh contains only quads and triangles.

@@

Alternatively the medial axis can be defined as the locations where the UoC surface is discontinuous,
or it can be defined as the locations where wave-front propagating from the outline shape make sharp corners. \cite{blum1967transformation}
This last conceptualization is especially relevant because the naive toolpath generation method consists precisely in equidistant wave-fronts from the outline.
The medial axis can therefore be seen as the space within which contour following toolpaths are generated.
See \cref{MAT_explanation}.

@@

\begin{figure}
\centering
\begin{subfigure}{0.3\columnwidth}
\centering
\includegraphics[height=1.5\columnwidth]{sources/method/MAT_explanation_circles.pdf}
\caption{Circles}
\label{MAT_explanation_circles}
\end{subfigure}
\begin{subfigure}{0.3\columnwidth}
\centering
\includegraphics[height=1.5\columnwidth]{sources/method/MAT_explanation_wavefronts.pdf}
\caption{Wave-fronts}
\end{subfigure}
\begin{subfigure}{0.3\columnwidth}
\centering
\includegraphics[height=1.5\columnwidth]{sources/method/MAT_explanation_cones.pdf}
\caption{Union of Cones}
\end{subfigure}
\caption{
Medial axis representations.
The medial axis can be defined in terms of the the number of support points of the inscribed circles,
as the pinch sites in wave-fronts
or as ridges in a volume defined by the union of cones.
}
\label{MAT_explanation}
\end{figure}

\begin{figure}\centering
\setlength{\figwidth}{0.24\columnwidth}
\setlength{\figwidthTwo}{0.15\columnwidth}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\figwidthTwo]{sources/method/simple_skeleton_mat}
\caption{MAT}\label{shape_decomposition_mat}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\figwidthTwo]{sources/method/simple_skeleton_vd}
\caption{VD}\label{shape_decomposition_vd}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\figwidthTwo]{sources/method/simple_skeleton_st}
\caption{ST}\label{shape_decomposition_st}
\end{subfigure}
\begin{subfigure}{\figwidth}\centering
\includegraphics[width=\figwidthTwo]{sources/method/half_edge_datastructure.pdf}
\caption{Datastructure}\label{shape_decomposition_datastructure}
\end{subfigure}
\caption{
Skeletonization of an outline shape (black).
Relation between the medial axis (red), the limited Voronoi Diagram (red and green) and the Skeletal Trapezoidation (red, green and gray): MAT $\subset$ Limited VD $\subset$ ST.
}
\label{skeletonization_comparison}
\end{figure}

\subsubsection{Skeletal trapezoidation}
The MAT decomposes the outline shape into several complex shapes which we need to further decompose in order to have a mesh consisting only of quads and triangles.
We employ a shape decomposition proposed by \citeauthor{Ding2016a}. \cite{Ding2016a}
Each of the regions demarcated by the skeleton is further decomposed by adding radial bones from each node $v$ to its support $\text{sup}(v)$.
The resulting skeleton decomposes the outline shape into trapezoids and triangles.
We will therefore call this shape decomposition the \emph{Skeletal Trapezoidation} (ST).
(The concept of a trapezoidation conventionally allows for the degenerate case where a trapezoid resolves into a triangle. \cite{chazelle1984,fournier1984})
We represent such a skeleton in a standard half-edge data-structure.
See \cref{shape_decomposition_datastructure}.

@@

We then also discretize parabolic segments and segments generated by two concave outline vertices into segments approximately as long as some constant $d^\text{discretization}$.
See \cref{discretization} and the middle of \cref{shape_decomposition_st}.
That way we can approximate the feature radius $R$ in between the two nodes $v_0$ and $v_1$ of a bone in the ST by interpolating linearly between $R(v_0)$ and $R(v_1)$.
This makes the skeleton capture a discrete approximation of the radius function which is then used to determine the height of each node in the skeleton in order to generate the 3D mesh of the UoC.
%; see \cref{mat_3d}.
